### 2015-01-26 Docs/getting_started/getting_started.tex

If you don't already have a copy of \maestro, you can obtain one
via {\tt git}\footnote{{\tt git} is an open-source source code version control
system.  It is a standard part of any Linux distribution.  You may
need to use your system's package manager to install {\tt git} if it
is not already present} as:
\begin{verbatim}
git clone http://bender.astro.sunysb.edu/Maestro/staging/MAESTRO.git
\end{verbatim}
\maestro\ is under active development, so you will want to keep in 
sync with the changes by periodically pulling from the repository.  Simply
type
\begin{verbatim}
git pull
\end{verbatim}
in the {\tt MAESTRO/} directory.

@@

>>>>

If you don't already have a copy of \maestro, you can obtain one from
the project's {\sf github}
page: \url{https://github.com/BoxLib-Codes/MAESTRO}\, .  There are
several options: you can fork it directly on {\sf github} (recommended
if you intend to develop the code) or clone it using {\tt git} from
the project page.

\maestro\ is under active development, so you will want to keep in 
sync with the changes by periodically pulling from the repository.  Simply
type
\begin{verbatim}
git pull
\end{verbatim}
in the {\tt MAESTRO/} directory.

@@

This problem can also be run adaptively.  The \code{tag\_boxes.f90}
file in the problem directory tags cells for refinement if the
perturbational temperature, $T^\prime$, exceeds some threshold.
